Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-12 programming23/paper.tex
missing period

There is a rich body of work that uses IDE instrumentation to study programmers
(e.g.,~\cite{pgnwk-koli-2022,wk-icer-2019,hl-icse-2010,j-ieeesoft-2013,kje-ase-2010, mmlb-swvis-2014, ncvjd-ecoop-2013, rl-icse-2008, we-xp-2004}).
WatchDog records the time that programmers spend reading, writing, and testing
code~\cite{blpgz-icse-2016}.
TDD-Guide collects similar data to teach testing methods~\cite{mdk-xp-2008}.
The Blackbox project collects Java programs and has enabled
dozens of contributions to the area of CS education~\cite{bask-icer-2018,bkmu-sigcse-2014}.
Other logging-based studies of Java programs draw conclusions from compiler error
messages~\cite{bgimgm-cse-2016,dlc-iticse-2014}.
The GRUMPS telemetry system collected 4.7 million keystroke-level actions from
Ada learners~\cite{tkdmceg-ascilite-2003,tm-iticse-2004}.
None of the above are sufficiently private to work for Roblox Studio
The BitFit project counts notable events (compile program, ask for hint, etc.)
for Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
While it does operate in a transparent~\cite{transparent-telemetry} manner, it
only provides coarse-grained information that would be insufficient in our
study.

>>>>

There is a rich body of work that uses IDE instrumentation to study programmers
(e.g.,~\cite{pgnwk-koli-2022,wk-icer-2019,hl-icse-2010,j-ieeesoft-2013,kje-ase-2010, mmlb-swvis-2014, ncvjd-ecoop-2013, rl-icse-2008, we-xp-2004}).
WatchDog records the time that programmers spend reading, writing, and testing
code~\cite{blpgz-icse-2016}.
TDD-Guide collects similar data to teach testing methods~\cite{mdk-xp-2008}.
The Blackbox project collects Java programs and has enabled
dozens of contributions to the area of CS education~\cite{bask-icer-2018,bkmu-sigcse-2014}.
Other logging-based studies of Java programs draw conclusions from compiler error
messages~\cite{bgimgm-cse-2016,dlc-iticse-2014}.
The GRUMPS telemetry system collected 4.7 million keystroke-level actions from
Ada learners~\cite{tkdmceg-ascilite-2003,tm-iticse-2004}.
None of the above are sufficiently private to work for Roblox Studio.
The BitFit project counts notable events (compile program, ask for hint, etc.)
for Java~\cite{ekc-wccce-2016,anna-russo-kennedy-ms-2006}.
While it does operate in a transparent~\cite{transparent-telemetry} manner, it
only provides coarse-grained information that would be insufficient in our
study.
